---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summary.stats

<!-- badges: start -->
<!-- badges: end -->

The goal of summary.stats is to produce a text ready summary of a numeric vector with summary statistics, and to plot the distribution of a numeric variable of interest. It contains the function sum.stats.  

## Installation

summary.stats is not yet on CRAN. But, you can download it from this repository using the following R command: 

``` r
devtools::install_github("jacob5/summary.stats")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(summary.stats)
library(gapminder)
sum_stats(gapminder, gapminder$lifeExp)
```

This package is special because it produces a string in text format which is easy to incorporate into a sentence, and quickly visualizes data distribution. 

```{r}
library(palmerpenguins)
sum_stats(penguins, penguins$bill_length_mm)
sum_stats(penguins, penguins$year)
```

